Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-07 benevol/paper.tex
Introduction and abstract

We find that, when taking into account contextual information in our clone detection, we find 11\% fewer clones. Manually inspecting the difference, we find that they are less relevant for refactoring.
\end{abstract}

@@

\section{Introduction}
%Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}. Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
Duplicate code fragments are often considered as symptoms of bad design~\cite{fowler2018refactoring}. They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software. Changing one occurrence of a duplicated fragment may require changes in other occurrences ~\cite{ostberg2014automatically}. Also, duplicated code was shown to account for 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.

@@

We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account this contextual information. We run the tool over a corpus of 2,267 Java projects. We find that taking into account contextual information results in 11\% less clones than found when not taking this information into account. Manually inspecting a sample the difference, we find that all clones with different contextual information in our sample are less relevant for refactoring.

>>>>

We find that, when taking into account contextual information in our clone detection, 11\% fewer clones are found. Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.
\end{abstract}

@@

\section{Introduction}
%Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}. Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}. They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}. Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}. Furthermore, duplicated code was shown to account for up to 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.

@@

We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account such contextual information. We run the tool over a corpus of 2,267 Java projects. We find that taking into account contextual information results in 11\% less clones than found when not taking this information into account. Manually inspecting a sample the difference, we find that all clones with different contextual information in our sample are less relevant for refactoring.
